Xinhua, Diplomacy, and Chinese Foreign Aid

### 2022-02-17 04_paper/draft1.Rmd
adding vdem to the dataset

However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "south-south cooperation" (get cite). While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. So, absent transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition Xinhua news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of Xinhua and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.

>>>>

However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "south-south cooperation" (get cite). While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition Xinhua news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of Xinhua and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage. This work further helps in dispelling the notion that China engages in development finance in secret.
